NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-06 paper/Chapters/Chapter3.tex
hypetension tab1 added

	\caption{\label{tab:daylevel}Day level latent class solution for three classes solution. (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating any food & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating any food & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating any food & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating any food & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating any food & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed $\geqslant$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{}\\ 
	\end{tabular}
\end{table}

@@

	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lcccc}
		\hiderowcolors
		\toprule
		& \textbf{\Centerstack{High carbo-\\hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}} & \textbf{\textit{P} value}\textsuperscript{*}\\
		\midrule
		\showrowcolors
		Counts (\%) & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
		Country (\%) &  &  &  & < 0.001\\
		\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
		\hspace{1em}Northern Ireland & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
		\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
		\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
		Day of Week (\%) &  &  &  & < 0.001\\
		\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
		\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
		\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
		\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
		\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
		\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
		\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
		\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
		Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
		Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
		Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
		Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
		Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
		Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
		Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
		Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
		Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
		Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
		\bottomrule
		\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\
		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\
		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose}}\\ 
		\multicolumn{5}{l}{{\scriptsize and sglucose syrups, sugars added to food and sugars in fruit juices.}}\\
	\end{tabular}
\end{table}

@@

The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}. Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007). Gender distribution across the three types of carbohydrate eaters were fairly even (\textit{p} = 0.119). Distribution of the carbohydrate eaters types was changing with the year of survey. Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year. Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year of the survey, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015). There was no evidence of

@@

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Countries (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household Income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni}}\\ 
	\multicolumn{5}{l}{{\scriptsize correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences between}}\\
	\multicolumn{5}{l}{{\scriptsize  latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}} \\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.} }\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil}} \\
	\multicolumn{5}{l}{{\scriptsize partnership.}}\\
\end{tabular}

@@

difference in employment status across three types of carbohydrate eaters. However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); low carbohydrate eaters were with the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.

Weighted means, percentages of anthropometric measurements, average of main nutrient intake as well as biochemical characteristic profiles of latent carbohydrate eaters groups are given in \textbf{Table \ref{tab:tab2}}. Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (94.6 cm) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 92.3, 92.2 cm in moderate and high carbohydrate eaters. High carbohydrate eaters had the lowest prevalence of being a current smoker (17.1\%). Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group. As expected, the mean total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively. Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but only 40.6\% in the low carbohydrate eaters. It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).

From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the number in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011). Borderline significance (\textit{p} = 0.051) suggested that fasting blood glucose level may be slightly higher in low carbohydrate eaters. Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.

@@

		Hypertension\textsuperscript{\dag}, Yes (\%) & 33.4 (29.9, 37.1) & 21.1 (17.7, 24.9) & 31.2 (28.3, 34.2) & < 0.001\\

>>>>

	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating any food & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating any food & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating any food & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating any food & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating any food & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed $\geqslant$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{}\\ 
	\end{tabular}
\end{table}

@@

	\caption{\label{tab:day-level-features}Means (standard deviations), and counts (\%) of the characteristics of different types of days according to carbohydrate intake.}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lcccc}
		\hiderowcolors
		\toprule
		& \textbf{\Centerstack{High carbo-\\hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}} & \textbf{\textit{P} value}\textsuperscript{*}\\
		\midrule
		\showrowcolors
		Counts (\%) & 9667 (39.5) & 5002 (20.4\%) & 9814 (40.1\%) & \\
		Country (\%) &  &  &  & < 0.001\\
		\hspace{1em}England & 5627 (58.2) & 2972 (59.4) & 5291 (53.9) & \\
		\hspace{1em}Northern Ireland & 1194 (12.4) & 527 (10.5) & 1400 (14.3) & \\
		\hspace{1em}Scotland & 1527 (15.8) & 813 (16.3) & 1774 (18.1) & \\
		\hspace{1em}Wales & 1318 (13.6) & 690 (13.8) & 1349 (13.7) & \\
		Day of Week (\%) &  &  &  & < 0.001\\
		\hspace{1em}Monday & 1303 (13.5) & 715 (14.3) & 1370 (14.0) & \\
		\hspace{1em}Tuesday & 1266 (13.1) & 674 (13.5) & 1290 (13.1) & \\
		\hspace{1em}Wednesday & 1225 (12.7) & 740 (14.8) & 1233 (12.6) & \\
		\hspace{1em}Thursday & 1272 (13.2) & 752 (15.0) & 1425 (14.5) & \\
		\hspace{1em}Friday & 1458 (15.1) & 797 (15.9) & 1479 (15.1) & \\
		\hspace{1em}Saturday & 1537 (15.9) & 703 (14.1) & 1495 (15.2) & \\
		\hspace{1em}Sunday & 1605 (16.6) & 621 (12.4) & 1522 (15.5) & \\
		\hspace{1em}Weekend, Yes (\%) & 3142 (32.5) & 1324 (26.5) & 3017 (30.7) & < 0.001\\
		Total energy (kJ) & 7539.98 (2875.87) & 7160.22 (2922.15) & 7439.68 (2978.91) & < 0.001\\
		Carbohydrate (g) & 222.79 (89.84) & 209.70 (86.17) & 206.59 (84.42) & < 0.001\\
		Protein (g) & 71.36 (29.79) & 69.55 (30.20) & 73.29 (32.94) & < 0.001\\
		Fat (g) & 65.44 (33.27) & 63.94 (33.76) & 67.24 (34.73) & < 0.001\\
		Alcohol (g) & 11.76 (27.31) & 8.85 (24.25) & 13.80 (33.00) & < 0.001\\
		Total sugars (g) & 98.63 (56.03) & 88.03 (50.50) & 86.39 (50.96) & < 0.001\\
		Starch (g) & 124.07 (55.84) & 121.59 (56.13) & 120.11 (54.62) & < 0.001\\
		Non-milk extrinsic sugar\textsuperscript{\dag} & 59.45 (49.31) & 50.07 (43.41) & 50.41 (44.84) & < 0.001\\
		Fruit (g) & 107.40 (137.97) & 103.15 (129.08) & 92.76 (126.02) & < 0.001\\
		Yellow Red Green Vegetables (g) & 26.52 (46.44) & 26.84 (47.99) & 26.16 (45.99) & 0.681\\
		\bottomrule
		\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from Pearson $\chi^2$ test for categorical variables, and one-way ANOVA comparing the means}}\\
		\multicolumn{5}{l}{{\scriptsize  in multiple groups for continuous variables;}}\\
		\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Non-milk extrinsic sugar is defined as: additionally added free sugar, such as table sugar, honey, glucose, fructose}}\\ 
		\multicolumn{5}{l}{{\scriptsize and glucose syrups, sugars added to food and sugars in fruit juices.}}\\
	\end{tabular}
\end{table}

@@

The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}. Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001), and slightly less from England (\textit{p} = 0.007). Gender distribution across the three types of carbohydrate eaters were fairly even (\textit{p} = 0.119). Distribution of the carbohydrate eater types was changing with the year of survey. Low carbohydrate eaters represented 32.5\% of the population in the first year of survey, but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year. Proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year of the survey, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015). There was no evidence of

@@

\begin{tabular}[t]{lcccc}
	\hiderowcolors
	\toprule
	\textbf{Variables} & \textbf{\Centerstack{Low carbo-\\hydrate eaters\\(n = 1730)}} & \textbf{\Centerstack{Moderate carbo-\\hydrate eaters\\(n = 1772)}} & \textbf{\Centerstack{High carbo-\\hydrate eaters\\(n = 2653)}} & \textbf{\textit{P} value} \textsuperscript{*}\\
	\midrule
	\showrowcolors
	Total (\%) & 28.4 (26.9, 29.9) & 28.7 (27.1, 30.3) & 43.0 (41.3, 44.7) & \\
	Country (\%) &  &  &  & 0.007\\
	\hspace{1em}England & 84.5 (81.7, 86.9) & 82.0 (79.3, 84.5) & 84.7 (82.3, 86.8) & \\
	\hspace{1em}Northern Ireland & 2.1 (1.6, 2.8) & 4.2 (3.2, 5.6) & 2.2 (1.7, 3.0) & \\
	\hspace{1em}Scotland & 9.1 (7.0, 11.8) & 8.6 (6.7, 11.1) & 8.0 (6.3, 10.2) & \\
	\hspace{1em}Wales & 4.3 (3.3, 5.6) & 5.1 (4.0, 6.4) & 5.1 (4.0, 6.4) & \\
	Age (years) & 51.0 (49.9, 52.1) & 40.3 (39.1, 41.6) & 51.7 (50.7, 52.7) & < 0.001\\
	Sex (\%) &  &  &  & 0.119\\
	\hspace{1em}Men & 50.0 (46.9, 53.1) & 50.2 (47.0, 53.5) & 46.6 (44.0, 49.1) & \\
	\hspace{1em}Women & 50.0 (46.9, 53.1) & 49.8 (46.5, 53.0) & 53.4 (50.9, 56.0) & \\
	Survey years (\% in rows) &  &  &  & 0.015\\
	\hspace{1em}1 & 32.5 (28.4, 36.9) & 26.3 (21.9, 31.2) & 41.2 (36.6, 46.0) & \\
	\hspace{1em}2 & 26.8 (22.6, 31.3) & 22.6 (18.6, 27.3) & 50.6 (45.8, 55.4) & \\
	\hspace{1em}3 & 22.6 (18.8, 26.9) & 33.7 (28.6, 39.2) & 43.6 (38.7, 48.7) & \\
	\hspace{1em}4 & 27.9 (24.1, 32.2) & 27.6 (23.8, 31.8) & 44.4 (40.2, 48.7) & \\
	\hspace{1em}5 & 27.9 (24.2, 32.0) & 28.7 (24.4, 33.5) & 43.3 (38.2, 48.6) & \\
	\hspace{1em}6 & 28.0 (24.0, 32.4) & 31.5 (26.9, 36.6) & 40.5 (35.8, 45.3) & \\
	\hspace{1em}7 & 29.1 (25.2, 33.4) & 29.0 (24.5, 34.0) & 41.8 (37.1, 46.7) & \\
	\hspace{1em}8 & 31.1 (27.3, 35.3) & 30.5 (25.9, 35.5) & 38.4 (34.1, 42.8) & \\
	Paid employment\textsuperscript{\dag} (\%) &  &  &  & 0.907\\
	\hspace{1em}Yes & 40.3 (37.0, 43.6) & 40.8 (37.1, 44.5) & 39.8 (37.1, 42.6) & \\
	\hspace{1em}No & 59.7 (56.4, 63.0) & 59.2 (55.5, 62.9) & 60.2 (57.4, 62.9) & \\
	Live with partner\textsuperscript{\ddag} (\%) &  &  &  & < 0.001\\
	\hspace{1em}Yes & 56.9 (53.6, 60.1) & 38.4 (35.2, 41.8) & 61.3 (58.7, 63.7) & \\
	\hspace{1em}No & 43.1 (39.9, 46.4) & 61.6 (58.2, 64.8)) & 38.7 (36.3, 41,3) & \\
	Household Income, \textsterling/year & \Centerstack{36558.5\\(34800.2, 38316.8)} & \Centerstack{27180.8\\(25597.9, 28763.7)} & \Centerstack{32171.6\\(31024.9, 33318.2)} & < 0.001\\
	Ethnicity (\%) &  &  &  & \\
	\hspace{1em}White & 94.2 (92.4, 95.6) & 79.5 (76.4, 82.3) & 91.9 (90.1, 93.4) & < 0.001\\
	\hspace{1em}Non-White & 5.8 (4.4, 7.6) & 20.5 (17.7, 23.6) & 8.1 (6.6, 9.9) & \\
	Education (\%) &  &  &  & \\
	\hspace{1em}Degree or higher & 29.0 (26.1, 32.1) & 23.3 (20.5, 26.3) & 26.2 (24.1, 28.5) & 0.019\\
	\hspace{1em}Lower than degree & 71.0 (67.9, 73.9) & 76.7 (73.7, 79.5) & 73.8 (71.5, 75.9) & \\
	\bottomrule
	\multicolumn{5}{l}{{\scriptsize \textit{Note: }}}\\
	\multicolumn{5}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
	\multicolumn{5}{l}{{\scriptsize Variables were weighted by individual weights.}}\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{*} For continuous variables, the \textit{F} test was used to determine differences between latent classes with Bonferroni}}\\ 
	\multicolumn{5}{l}{{\scriptsize correction to account for multiple testing across $>$ 2 classes. For categorical variables, differences between}}\\
	\multicolumn{5}{l}{{\scriptsize  latent classes were assessed using the adjusted Pearson $\chi^2$ test for survey data.}} \\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\dag} Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey.} }\\
	\multicolumn{5}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil}} \\
	\multicolumn{5}{l}{{\scriptsize partnership.}}\\
\end{tabular}

@@

difference in employment status across three types of carbohydrate eaters. However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with a partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.

Weighted means, percentages of anthropometric measurements, average of main nutrient intake, as well as biochemical characteristic profiles of latent carbohydrate eater groups are given in \textbf{Table \ref{tab:tab2}}. Low carbohydrate eaters were with higher BMI (27.8 kg/m\textsuperscript{2}) and larger WC (98.9/89.9 cm in men/women) compared with 27.2, 27.3 kg/m\textsuperscript{2}, and 95.9/88.7 (men/women), 98.1/87.2 (men/women) cm in moderate and high carbohydrate eaters. Moderate carbohydrate eaters had the highest prevalence of being a current smoker (27.8\%), shortest physical activity (geometric mean: 0.87 hours/day), and the lowest prevalence of hypertension (20.2\%).

Average total energy intake over the 4 days of dietary survey was the highest (7985.8 kJ) in the low carbohydrate eaters group. As expected, the mean total carbohydrate intake was 203.8 g, 218.3 g, and 233.4 g for low, moderate, and high carbohydrate eaters, respectively. Energy contribution from carbohydrate was close to 50\% in the high carbohydrate eaters, but was only 40.6\% in the low carbohydrate eaters. It is noteworthy that low carbohydrate eaters consumed the highest average amount of protein (79.9 g, 17.2\% of total energy), fat (74.7g, 35.4\% of total energy), and alcohol (20.8 g, 6.8\% of total energy).

From the results of blood tests, 6.9\% of low carbohydrate eaters were found to be diabetes (diagnosed by A1C > 6.5\%), while the percentages of diabetes in the moderate and high carbohydrate eaters were 3.5\%, and 4.1\% (\textit{p} < 0.011). There were some evidence (\textit{p} = 0.027) that fasting blood glucose level may be slightly higher in non-diabetes low carbohydrate eaters, while the geometric mean for A1C was probably lower in moderate carbohydrate eaters (4.72, 95\%CI: 5.39, 5.47). Cholesterol, HDL, and LDL were all lower in the moderate carbohydrate eaters, while no evidence of any difference of TG was found across three types of carbohydrate eaters.

@@

		Physical activity (hours/day) \textsuperscript{\P} & 1.08 (0.97, 1.19) & 0.87 (0.77, 0.97)  & 1.07 (0.98, 1.16) & 0.005 \\
